Moral Foundations of U.S. Political News Organizations

### 2019-03-19 pilot_manuscript.Rmd
not sure what this thing is doing
making some progress

````{r NPR, eval = F, include = F}
urlslist_final = c()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:2){ ##change this to 50
  url2 = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
  webpage2 = read_html(url2)
  headline_data2 = html_nodes(webpage2,'.title')

  #URLs
  attr_data2 = html_attrs(headline_data2) 
  urlslist2 = unlist(attr_data2)
  urlslist2 = urlslist2[grep("http", urlslist2)]

  #add them to an overall
  urlslist_final = c(urlslist_final, urlslist2)

  Sys.sleep(runif(1, 1, 5))
}

@@

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 5))
} ##end for loop
```

>>>>

````{r NPR, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = c()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:2){ ##change this to 50

  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)

  #get the page source
  webpage <-remDr$getPageSource()

  #pull the links
  headline_data = html_nodes(webpage2,'a')
  attr_data = html_attrs(headline_data)

  #deal with the links
  urlslist = unlist(attr_data)
  urlslist = urlslist[grep("^/201", urlslist)]
  urlslist = unique(urlslist)

  #combine into one list
  urlslist_final = c(urlslist, urlslist_final)

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

} #close the loop

@@

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 5))
} ##end for loop
